---
title: "p8105_hw5_smm2350"
author: "Shaina Mackin"
date: "11/20/2021"
output: github_document
---

# Homework 5

To begin, I'll load libraries, set the seed, and set the theme.

```{r setup, include=FALSE}
library(tidyverse)
library(rvest)

set.seed(1)

theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

For this problem, we are interested in data gathered and made publicly available by _The Washington Post_ on homicides in 50 large U.S. cities. In the below code chunk, I import and clean the data: 

```{r}
homicide_df = 
  read_csv("./homicide_data/homicide-data.csv", na = c(" ", "Unknown")) %>%
  mutate(
    city_state = str_c(city, state), 
    resolution = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved"
    )) %>%
  relocate(city_state) %>%
  filter(city_state != "TulsaAL")
```

The data set contains `r nrow(homicide_df)` observations and `r ncol(homicide_df)` variables,  for a total of `r (nrow(homicide_df)*ncol(homicide_df))` data points. 

For the city of Baltimore, MD, we now use the `prop.test` function to estimate the proportion of homicides that are unsolved: 

```{r}
baltimore_df = 
  homicide_df %>%
  filter(city_state == "BaltimoreMD")

baltimore_summary = 
  baltimore_df %>%
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  )

baltimore_test = 
  prop.test(
  x = baltimore_summary %>% pull(unsolved),
  n = baltimore_summary %>% pull(n))

baltimore_test %>%
  broom::tidy()
```

Next, we iterate across some additional cities: 

```{r}
prop_test_function = function(city_df) {
  
  city_summary = 
    city_df %>%
    summarize(
      unsolved = sum(resolution == "unsolved"),
      n = n()
    )
  
  city_test = 
    prop.test(
      x = city_summary %>% pull(unsolved),
      n = city_summary %>% pull(n))
    
  return(city_test)
}

prop_test_function(baltimore_df)

homicide_df %>%
  filter(city_state == "AlbuquerqueNM") %>%
  prop_test_function()
```

Now, we iterate across all cities:

```{r}
results_df =
  homicide_df %>%
  nest(data = uid:resolution) %>%
  mutate(
    test_results = map(data, prop_test_function),
    tidy_results = map(test_results, broom::tidy)
  ) %>%
  select(city_state, tidy_results) %>%
  unnest(tidy_results) %>%
  select(city_state, estimate, starts_with("conf"))

nested_df = 
  homicide_df %>% 
  nest(data = uid:resolution) %>% 
  mutate(
    test_results = map(data, prop_test_function),
    tidy_results = map(test_results, broom::tidy)
  )

nested_df %>%
  filter(city_state == "BaltimoreMD") %>%
  pull(tidy_results)
```

Finally, we are interested in making a plot to show estimates and confidence intervals for each city: 

```{r}
results_df %>%
  mutate(city_state = fct_reorder(city_state, estimate)) %>%
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

```{r}
homicide_df %>%
  group_by(city_state) %>%
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  ) %>%
  mutate(
    test_results = map2(unsolved, n, prop.test),
    tidy_results = map(test_results, broom::tidy)
  ) %>%
  select(city_state, tidy_results) %>%
  unnest(tidy_results) %>%
  select(city_state, estimate, starts_with("conf")) 
```

## Problem 2

For this problem, we are interested in the data from a longitudinal study that included a control arm and an experimental arm.

First, I'll create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time. I'll do this by:
</br>
• Starting with a dataframe containing all file names
</br>
• Iterating over file names and reading in data for each subject
</br>
• Tidying the result; manipulating file names to include control arm and subject ID and making sure weekly observations are “tidy”

```{r}
study_df = 
tibble(
  files = list.files("./data")) %>% 
  mutate(
    data = map(files, ~ read_csv(file.path("./data", .)))
  ) %>% 
  unnest(data) %>%
  separate(files, into = c("study_arm", "subject_id"), sep="_", extra = "merge") %>%
  mutate(
    subject_id = gsub("[A-z]","", subject_id)) %>%
  mutate(
    subject_id = gsub('[.]', "", subject_id)) %>%
    pivot_longer(
      cols = starts_with("week"),
    names_to = "week",
    values_to = "value",
    values_drop_na = TRUE
  ) %>%
  mutate(
    week = gsub("[A-z]","", week)) %>%
  mutate(
    study_arm = if_else(study_arm == "con", "control", "experiment"))
```

Finally, I'll make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.

```{r}
study_df %>%
  ggplot(aes(x = as.numeric(week), y = as.numeric(value), color = subject_id)) +
    geom_line() +
  labs(
    title = "Subject Values Across Study Arms Over Time",
    x = "Week",
    y = "Value",
    color = "Subject ID"
  ) +
  facet_grid(cols = vars(study_arm))
```


## Problem 3

```{r}
library(tidyverse)

set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

Write a function: 

```{r}
fill_in_missing = function(vector) {
  
  if(is.numeric) {
    
    ...

  }
  
  if(is.character) {
    
    ...
    
  }
  
}
```


